### 2019-03-21 report/MSc_Report.tex
Small

In science, there is not only a need for accumulation of knowledge, but also for concentration. For the same reason as statistical analysis is performed on single experiments, it can also be used for results of multiple experiments or studies: to simplify and summarize the data at hand to a degree that is understandable for humans. The latter procedure goes usually under the term of meta-analysis. Meta analyses are used to summarize results and evidence over multiple studies when they are considered to be similar enough.

\vspace{0mm}
In the face of the large amount of research that is done in some fields of empirical science, meta-analysis becomes increasingly important, for looking at all evidence would simply take very long for one person. Meta-analysises are often part of a systematic review, an effort of experts of a field to provide an overlook over the evidence. In the course of a review, all literature and data with respect to a scientific question is collected and a meta-analysis is operated at the end to summarize the findings.

@@

\vspace{0mm}
However, there are problems that potentially limit the validity of meta-analysis; studies at hand can be biased or heterogeneity between study results can be large and the number of studies small. The importance and the issues of meta-analysis are the reasons why they have been chosen as one general topic of the masters thesis. One particular problem will furthermore be investigated in more detail: reporting bias and meta-analysis. Not only will the methods to deal with issues as reporting bias be discussed, but also will they be applied on a dataset of systematic reviews that can be used for meta-analysis. So at the end of the report, the reader will not only have an impression of the technical issues caused by reporting bias, but also of the abundance and extent of it in the dataset. Since the dataset is very large and of good quality, results might be again be generalizable to some extent to reporting bias in clinical science in general.

@@

\vspace{0mm}
The data analyzed in this thesis stems completely from the Cochrane Library of systematic Reviews (cite). The reviews are arguably of good quality, since the authors are following elaborated guidelines, and there are control-mechanisms within the organisation that should prohibit conflicts of interests. This might further improve the validity and precision of findings and conclusions that have been made based on this data.

@@

% latex table generated in R 3.5.1 by xtable 1.8-3 package
% Thu Mar 21 11:15:04 2019
\begin{table}[ht]
\centering
\begingroup\scriptsize
\begin{tabular}{lllrrrr}
  \hline
Study & Comparison\_type & Outcome & Events & Total & Events\_c & Total\_c \\ 
  \hline
Bohn 1989 & Barbiturate vs no barbiturate & Death at the end of follow-up &  11 &  41 &  11 &  41 \\ 
  Ward 1985 & Barbiturate vs no barbiturate & Death at the end of follow-up &  14 &  27 &  13 &  26 \\ 
   \hline
\end{tabular}
\endgroup
\caption{Example of two comparisons as given in the dataset. Events denotes the count of events in the treatment group while Events c the count of events in the group compared to. Further descriptive variables have been ommitted} 
\label{barbiturate.row}
\end{table}

@@

\begin{table}[ht]
  \begin{center}
    \begin{tabular}{l l}
      \textbf{Variable} & \textbf{Description}\\
      \hline
      \textbf{File name} & The name of the file from which the review data has been . \\&gathered. This file corresponds to a file available in the. \\& Cochrane library\\
      \textbf{doi} & Digital object identifier. A unique id of the review such that  \\ &the full text of the review can be found on the web.\\
      \textbf{File index} & Internal index of the file in the Cochrane library.\\
      \textbf{File version} & Denotes the version of the review, since the reviews are \\ &occasionally updated.\\
      %\multicolumn{2}{c}{textbf{Study level variables}}\\ 
      \hline
      \textbf{Comparison type} & Specification of the interventions compared in the study\\
      \textbf{Outcome} & Specification by which outcome the interventions are compared\\
      \textbf{Subgroup} & Potentially indication of affiliation to subgroups\\
      \textbf{Study name} & Name of the study to which the comparison belongs\\
      \textbf{Study publication year} & Year in which the study was published\\
      \textbf{Outcome measure} & Indication of the quantification method of the effect \\ &(of one intervention compared to the other).\\
      \textbf{Effect} & Measure of the effect given in the quantity denoted by \\ &``outcome measure''.\\
      \textbf{Events (1/2)} & The counts of patients with an outcome \textit{if}\\ & measurement/outcome is binary or dichotomous \\ &2 (1 for treatment group and 2 for control group).\\
      \textbf{Total (1/2)} & Number of patients in groups.\\
      \textbf{Mean (1/2)} & Mean of patient measurements \textit{if} outcome is continuous.\\
      \textbf{Standard deviation (1/2)} & Standard deviation of mean \textit{if} \\ &outcome is continuous.
    \end{tabular}
  \caption{Dataset variable descriptions}
  \label{variable}
  \end{center}
\end{table}

The structure of a hypothetical review is shown in Figure \ref{review}. 
% Comparisons of a review can consecutively be subdivided into different comparison types, different outcome measures and different subgroups. 
The comparison type variable specifies what is compared, the outcome variable how it is compared, and the subgroup variable indicates if the comparison belongs to a certain subgroup. If desired, Figure \ref{review} can be compared to Table \ref{barbiturates} where an examplary review is listed.

\begin{figure}
\tikzstyle{every node}=[draw=black,thick,anchor=west]
\tikzstyle{selected}=[draw=red,fill=red!30]
\tikzstyle{optional}=[dashed,fill=gray!50]
\begin{tikzpicture}
[grow = right, anchor = west, 
  growth parent anchor=east, % added code
  parent anchor=east]
  \node {Review} [edge from parent fork right]
    child { node {Comparison type 2}
      child { node {Outcome 2}}
      child { node {Outcome 1}
        child { node {Subgroup 2}}
        child { node {Subgroup 1}}}
    }
    child [missing] {}		
    child { node {Comparison type 1  }};
\end{tikzpicture}
\caption{Structure of a hypothetical review with two different comparisons.}
\label{review.structure}
\end{figure}

@@

% latex table generated in R 3.5.1 by xtable 1.8-3 package
% Thu Mar 21 11:15:04 2019
\begin{table}[ht]
\centering
\begingroup\footnotesize
\begin{tabular}{lll}
  \hline
Study & Comparison & Outcome \\ 
  \hline
Bohn 1989 & Barbiturate vs no barbiturate & Death at the end of follow-up \\ 
  Bohn 1989 & Barbiturate vs no barbiturate & Death or severe disability at the end of follow-up \\ 
  Eisenberg 1988 & Barbiturate vs no barbiturate & Death at the end of follow-up \\ 
  Eisenberg 1988 & Barbiturate vs no barbiturate & Uncontrolled ICP during treatment \\ 
  Eisenberg 1988 & Barbiturate vs no barbiturate & Hypotension during treatment \\ 
  Perez-Barcena 2008 & Pentobarbital vs Thiopental & Death at the end of follow-up (6 months) \\ 
  Perez-Barcena 2008 & Pentobarbital vs Thiopental & Death or severe disability at the end of follow-up (6 months) \\ 
  Perez-Barcena 2008 & Pentobarbital vs Thiopental & Uncontrolled ICP during treatment \\ 
  Perez-Barcena 2008 & Pentobarbital vs Thiopental & Hypotension during treatment \\ 
  Schwartz 1984 & Barbiturate vs Mannitol & Death at the end of follow-up (1 year) \\ 
  Schwartz 1984 & Barbiturate vs Mannitol & Death at the end of follow-up (1 year) \\ 
  Schwartz 1984 & Barbiturate vs Mannitol & Uncontrolled ICP during treatment \\ 
  Ward 1985 & Barbiturate vs no barbiturate & Death at the end of follow-up \\ 
  Ward 1985 & Barbiturate vs no barbiturate & Death or severe disability at the end of follow-up \\ 
  Ward 1985 & Barbiturate vs no barbiturate & Mean ICP during treatment \\ 
  Ward 1985 & Barbiturate vs no barbiturate & Mean arterial pressure during treatment \\ 
  Ward 1985 & Barbiturate vs no barbiturate & Hypotension during treatment \\ 
  Ward 1985 & Barbiturate vs no barbiturate & Mean body temperature during treatment \\ 
   \hline
\end{tabular}
\endgroup
\caption{Barbiturate and head injury review. In the columns, study names, comparison types and outcome measure of the comparisons are given.} 
\label{barbiturates}
\end{table}

@@

\vspace{0mm}
Having provided a rough overview over the dataset, now, some more specific information is provided. The dataset consists of 463820 comparisons and has 25 variables that specify the comparisons. The abundancy of some missing values in the dataset is given in Table \ref{missing}. For variables as research subject, outcome and subgroup name and event counts there are no missing values. The relative abundancy of missing values is very low except for study years.

% latex table generated in R 3.5.1 by xtable 1.8-3 package
% Thu Mar 21 11:15:04 2019
\begin{table}[ht]
\centering
\begingroup\footnotesize
\begin{tabular}{lr}
  \hline
  \hline
Missing mean values & 1287 \\ 
  Missing standard deviations & 999 \\ 
  Missing effects & 158 \\ 
  Missing study year & 27234 \\ 
   \hline
\end{tabular}
\endgroup
\caption{Number of missing variables and measurements in the dataset.} 
\label{missing}
\end{table}

@@

\end{knitrout}
\caption{Frequencies of study publication years in the dataset. 44655 were excluded due to likely wrong indications.}
\label{study.years}
\end{figure}

Figure \ref{study.outcomes} provides the frequencies of outcome types of the comparisons. Note that the abundancy of mean differences and standardized mean differences can also give an impression of the proportion of continuous outcome comparisons vs. binary outcome comparisons in the dataset.

@@

\end{knitrout}
\caption{Frequencies of some outcome measures for the effects in the dataset. 5593 measures with other outcome measures are excluded.}
\label{study.outcomes}
\end{figure}

@@

\end{knitrout}
\caption{Empirical distribution of number of studies per review.}
\label{studies.per.review}
\end{figure}

@@

\end{knitrout}
\caption{Empirical distribution of number of comparisons per review.}
\label{comparisons.per.review}
\end{figure}

@@

\end{knitrout}
\caption{Empirical distribution of number of different research subjects per review.}
\label{subjects.per.review}
\end{figure}

@@

% latex table generated in R 3.5.1 by xtable 1.8-3 package
% Thu Mar 21 11:15:10 2019
\begin{table}[ht]
\centering
\begingroup\footnotesize
\begin{tabular}{lll}
  \hline
n & Cumulative sum (without subgroups) & Cumulative sum (with subgroups) \\ 
  \hline
1 & 109177 & 186267 \\ 
  2 & 67685 & 83924 \\ 
  3 & 47786 & 52245 \\ 
  4 & 36155 & 36176 \\ 
  5 & 28077 & 26552 \\ 
  6 & 22689 & 20113 \\ 
  7 & 18536 & 15888 \\ 
  8 & 15466 & 12931 \\ 
  9 & 13000 & 10817 \\ 
  10 & 11001 & 9226 \\ 
  11 & 9356 & 7988 \\ 
  12 & 8052 & 7067 \\ 
  13 & 6984 & 6365 \\ 
  14 & 6041 & 5780 \\ 
  15 & 5325 & 5325 \\ 
   \hline
\end{tabular}
\endgroup
\caption{Cumulative number of groups with number of reproduction trials >= n} 
\label{repr.groups}
\end{table}

>>>>

In science, there is not only a need for accumulation of knowledge, but also for concentration. For the same reason as statistical analysis is performed on single experiments, it can also be used for results of multiple experiments or studies: to simplify and summarize the data at hand to a degree that is understandable. The latter procedure goes usually under the name of meta-analysis. Meta analyses are used to summarize results and evidence over multiple studies when they are considered to be similar enough.

\vspace{0mm}
In the face of the large amount of research that is done in some fields of empirical science, meta-analysis becomes increasingly important, for looking at all evidence would simply take very long for one person. Meta-analyses are often part of a systematic review, an effort of experts of a field to provide an overlook over the evidence. In the course of a review, all literature and data with respect to a scientific question is collected and a meta-analysis is operated at the end to summarize the findings.

@@

\vspace{0mm}
However, there are problems that potentially limit the validity of meta-analysis; studies at hand can be biased or heterogeneity between study results can be large and the number of studies small. The importance and the issues of meta-analysis are the reasons why they have been chosen as one general topic of the masters thesis. One particular problem will furthermore be investigated in more detail: reporting bias and meta-analysis. Not only will the methods to deal with issues as reporting bias be discussed, but also will they be applied on a dataset of systematic reviews that can be used for meta-analysis. So at the end of the report, the reader will not only have an impression of the technical issues caused by reporting bias, but also of the abundance and extent of it in the dataset. Since the dataset is very large and of good quality, results might also be representative to some extent for reporting bias in clinical science.

@@

\vspace{0mm}
The data analyzed in this thesis stems completely from the Cochrane Library of systematic Reviews (cite).

\vspace{0mm}
The reviews are arguably of good quality, since the authors are following elaborated guidelines, and there are control-mechanisms within the organisation that should prohibit conflicts of interests. This might further improve the validity and precision of findings and conclusions that have been made based on this data.

@@

% latex table generated in R 3.5.1 by xtable 1.8-3 package
% Thu Mar 21 12:54:57 2019
\begin{table}[ht]
\centering
\begingroup\scriptsize
\begin{tabular}{lllrrrr}
  \hline
Study & Comparison\_type & Outcome & Events & Total & Events\_c & Total\_c \\ 
  \hline
Bohn 1989 & Barbiturate vs no barbiturate & Death at the end of follow-up &  11 &  41 &  11 &  41 \\ 
  Ward 1985 & Barbiturate vs no barbiturate & Death at the end of follow-up &  14 &  27 &  13 &  26 \\ 
   \hline
\end{tabular}
\endgroup
\caption{Example of two comparisons as given in the dataset. Events denotes the count of events in the treatment group while Events c the count of events in the group compared to. Further descriptive variables have been ommitted} 
\label{barbiturate.row}
\end{table}

@@

\begin{table}[ht]
  \begin{center}
    \begin{tabular}{l l}
      \textbf{Variable} & \textbf{Description}\\
      \hline
      \textbf{File name} & The name of the file from which the review data has been . \\&gathered. This file corresponds to a file available in the. \\& Cochrane library\\
      \textbf{doi} & Digital object identifier. A unique id of the review such that  \\ &the full text of the review can be found on the web.\\
      \textbf{File index} & Internal index of the file in the Cochrane library.\\
      \textbf{File version} & Denotes the version of the review, since the reviews are \\ &occasionally updated.\\
      %\multicolumn{2}{c}{textbf{Study level variables}}\\ 
      \hline
      \textbf{Comparison type} & Specification of the interventions compared in the study\\
      \textbf{Outcome} & Specification by which outcome the interventions are compared\\
      \textbf{Subgroup} & Potentially indication of affiliation to subgroups\\
      \textbf{Study name} & Name of the study to which the comparison belongs\\
      \textbf{Study publication year} & Year in which the study was published\\
      \textbf{Outcome measure} & Indication of the quantification method of the effect \\ &(of one intervention compared to the other).\\
      \textbf{Effect} & Measure of the effect given in the quantity denoted by \\ &``outcome measure''.\\
      \textbf{Events (1/2)} & The counts of patients with an outcome \textit{if}\\ & measurement/outcome is binary or dichotomous \\ &2 (1 for treatment group and 2 for control group).\\
      \textbf{Total (1/2)} & Number of patients in groups.\\
      \textbf{Mean (1/2)} & Mean of patient measurements \textit{if} outcome is continuous.\\
      \textbf{Standard deviation (1/2)} & Standard deviation of mean \textit{if} \\ &outcome is continuous.
    \end{tabular}
  \caption{Dataset variable descriptions  \label{variable}}

  \end{center}
\end{table}

The structure of a hypothetical review is shown in Figure \ref{review}. 
% Comparisons of a review can consecutively be subdivided into different comparison types, different outcome measures and different subgroups. 
The comparison type variable specifies what is compared, the outcome variable how it is compared, and the subgroup variable indicates if the comparison belongs to a certain subgroup. If desired, Figure \ref{review} can be compared to Table \ref{barbiturates} where an exemplary review is listed.

\begin{figure}
\tikzstyle{every node}=[draw=black,thick,anchor=west]
\tikzstyle{selected}=[draw=red,fill=red!30]
\tikzstyle{optional}=[dashed,fill=gray!50]
\begin{tikzpicture}
[grow = right, anchor = west, 
  growth parent anchor=east, % added code
  parent anchor=east]
  \node {Review} [edge from parent fork right]
    child { node {Comparison type 2}
      child { node {Outcome 2}}
      child { node {Outcome 1}
        child { node {Subgroup 2}}
        child { node {Subgroup 1}}}
    }
    child [missing] {}		
    child { node {Comparison type 1  }};
\end{tikzpicture}
\caption{Structure of a hypothetical review with two different comparisons\label{review.structure}}
\label{review.structure}
\end{figure}

@@

% latex table generated in R 3.5.1 by xtable 1.8-3 package
% Thu Mar 21 12:54:57 2019
\begin{table}[ht]
\centering
\begingroup\footnotesize
\begin{tabular}{lll}
  \hline
Study & Comparison & Outcome \\ 
  \hline
Bohn 1989 & Barbiturate vs no barbiturate & Death at the end of follow-up \\ 
  Bohn 1989 & Barbiturate vs no barbiturate & Death or severe disability at the end of follow-up \\ 
  Eisenberg 1988 & Barbiturate vs no barbiturate & Death at the end of follow-up \\ 
  Eisenberg 1988 & Barbiturate vs no barbiturate & Uncontrolled ICP during treatment \\ 
  Eisenberg 1988 & Barbiturate vs no barbiturate & Hypotension during treatment \\ 
  Perez-Barcena 2008 & Pentobarbital vs Thiopental & Death at the end of follow-up (6 months) \\ 
  Perez-Barcena 2008 & Pentobarbital vs Thiopental & Death or severe disability at the end of follow-up (6 months) \\ 
  Perez-Barcena 2008 & Pentobarbital vs Thiopental & Uncontrolled ICP during treatment \\ 
  Perez-Barcena 2008 & Pentobarbital vs Thiopental & Hypotension during treatment \\ 
  Schwartz 1984 & Barbiturate vs Mannitol & Death at the end of follow-up (1 year) \\ 
  Schwartz 1984 & Barbiturate vs Mannitol & Death at the end of follow-up (1 year) \\ 
  Schwartz 1984 & Barbiturate vs Mannitol & Uncontrolled ICP during treatment \\ 
  Ward 1985 & Barbiturate vs no barbiturate & Death at the end of follow-up \\ 
  Ward 1985 & Barbiturate vs no barbiturate & Death or severe disability at the end of follow-up \\ 
  Ward 1985 & Barbiturate vs no barbiturate & Mean ICP during treatment \\ 
  Ward 1985 & Barbiturate vs no barbiturate & Mean arterial pressure during treatment \\ 
  Ward 1985 & Barbiturate vs no barbiturate & Hypotension during treatment \\ 
  Ward 1985 & Barbiturate vs no barbiturate & Mean body temperature during treatment \\ 
   \hline
\end{tabular}
\endgroup
\caption{Barbiturate and head injury review. In the columns, study names, comparison types and outcome measure of the comparisons are given} 
\label{barbiturates}
\end{table}

@@

\vspace{0mm}
Having provided a rough overview over the dataset, now, some more specific information is provided. The dataset consists of 463820 comparisons and has 25 variables that specify the comparisons. The abundance of some missing values in the dataset is given in Table \ref{missing}. For variables as research subject, outcome and subgroup name and event counts there are no missing values. The relative abundance of missing values is very low except for study years.

% latex table generated in R 3.5.1 by xtable 1.8-3 package
% Thu Mar 21 12:54:58 2019
\begin{table}[ht]
\centering
\begingroup\footnotesize
\begin{tabular}{lr}
  \hline
  \hline
Missing mean values & 1287 \\ 
  Missing standard deviations & 999 \\ 
  Missing effects & 158 \\ 
  Missing study year & 27234 \\ 
   \hline
\end{tabular}
\endgroup
\caption{Number of missing variables and measurements in the dataset} 
\label{missing}
\end{table}

@@

\end{knitrout}
\caption{Frequencies of study publication years in the dataset. 44655 were excluded due to likely wrong indications}
\label{study.years}
\end{figure}

Figure \ref{study.outcomes} provides the frequencies of outcome types of the comparisons. Note that the abundance of mean differences and standardized mean differences can also give an impression of the proportion of continuous outcome comparisons vs. binary outcome comparisons in the dataset.

@@

\end{knitrout}
\caption{Frequencies of some outcome measures for the effects in the dataset. 5593 measures with other outcome measures are excluded}
\label{study.outcomes}
\end{figure}

@@

\end{knitrout}
\caption{Empirical distribution of number of studies per review}
\label{studies.per.review}
\end{figure}

@@

\end{knitrout}
\caption{Empirical distribution of number of comparisons per review}
\label{comparisons.per.review}
\end{figure}

@@

\end{knitrout}
\caption{Empirical distribution of number of different research subjects per review}
\label{subjects.per.review}
\end{figure}

@@

% latex table generated in R 3.5.1 by xtable 1.8-3 package
% Thu Mar 21 12:55:03 2019
\begin{table}[ht]
\centering
\begingroup\footnotesize
\begin{tabular}{lll}
  \hline
n & Cumulative sum (without subgroups) & Cumulative sum (with subgroups) \\ 
  \hline
1 & 109177 & 186267 \\ 
  2 & 67685 & 83924 \\ 
  3 & 47786 & 52245 \\ 
  4 & 36155 & 36176 \\ 
  5 & 28077 & 26552 \\ 
  6 & 22689 & 20113 \\ 
  7 & 18536 & 15888 \\ 
  8 & 15466 & 12931 \\ 
  9 & 13000 & 10817 \\ 
  10 & 11001 & 9226 \\ 
  11 & 9356 & 7988 \\ 
  12 & 8052 & 7067 \\ 
  13 & 6984 & 6365 \\ 
  14 & 6041 & 5780 \\ 
  15 & 5325 & 5325 \\ 
   \hline
\end{tabular}
\endgroup
\caption{Cumulative number of groups with number of reproduction trials >= n} 
\label{repr.groups}
\end{table}

### 2019-03-21 report/chapter02.Rnw
Small

<<echo=FALSE, results='asis'>>=
tp1 <- arrange(filter(madata, file.nr == 21) %>% 
          select(Study = study.name, Comparison = comparison.name,Outcome = outcome.name), Study)
tp1[tp1$Study == "P\303\251rez-B\303\241rcena 2008", 1] = "Perez-Barcena 2008"
print(xtable(tp1, label = "barbiturates", caption = "Barbiturate and head injury review. In the columns, study names, comparison types and outcome measure of the comparisons are given."), include.rownames = F, size = "footnotesize")
@

@@

\vspace{0mm}
Having provided a rough overview over the dataset, now, some more specific information is provided. The dataset consists of \Sexpr{dim(madata)[1]} comparisons and has \Sexpr{dim(madata)[2]} variables that specify the comparisons. The abundancy of some missing values in the dataset is given in Table \ref{missing}. For variables as research subject, outcome and subgroup name and event counts there are no missing values. The relative abundancy of missing values is very low except for study years.

@@

print(xtable(missing.table, label = "missing", caption = "Number of missing variables and measurements in the dataset.", align = "lr"), include.colnames = F,
      size = "footnotesize", digits = 0)
@

@@

\begin{figure}
<<echo=FALSE>>=
madata %>% filter(study.year < 2019 & study.year > 1920) %>% ggplot(aes(x = study.year)) + geom_histogram(col = "gray15", fill = "dodgerblue") +
  theme_bw() + xlab("Year") + ylab("Study frequency")
@
\caption{Frequencies of study publication years in the dataset. 44655 were excluded due to likely wrong indications.}
\label{study.years}
\end{figure}

Figure \ref{study.outcomes} provides the frequencies of outcome types of the comparisons. Note that the abundancy of mean differences and standardized mean differences can also give an impression of the proportion of continuous outcome comparisons vs. binary outcome comparisons in the dataset.

\begin{figure}
<<echo=FALSE>>=
yodata %>% group_by(outcome.measure) %>% count() %>% arrange(desc(n)) %>% ungroup() %>% filter(row_number() < 9) %>% 
  ggplot(aes(x = outcome.measure, y = n)) +
  geom_col(col = "gray15", fill = "dodgerblue") +
  theme_bw() + ylab("Comparison frequency") + xlab("Outcome measure")
@
\caption{Frequencies of some outcome measures for the effects in the dataset. 5593 measures with other outcome measures are excluded.}
\label{study.outcomes}
\end{figure}

@@

\begin{figure}
<<echo=FALSE>>=
madata %>% group_by(file.nr) %>% distinct(study.name) %>% count() %>%
  filter(n < 50) %>%
  full_join( madata %>% group_by(file.nr) %>% distinct(study.name) %>% count %>%
               filter(n > 49) %>% mutate(n = 50)) %>%
  group_by(n) %>% count() %>%
  ggplot(aes(x = n, y = nn)) + geom_col(col = "gray15", fill = "dodgerblue") +
  theme_bw() + xlab("Study number") + ylab("Reviews Frequency")
@
\caption{Empirical distribution of number of studies per review.}
\label{studies.per.review}
\end{figure}

\begin{figure}
<<echo=FALSE>>=
madata %>% group_by(file.nr) %>% count() %>%
  filter(n < 50) %>%
  full_join( madata %>% group_by(file.nr) %>% distinct(comparison.name) %>% count %>%
               filter(n > 49) %>% mutate(n = 50)) %>%
  group_by(n) %>% count() %>%
  ggplot(aes(x = n, y = nn)) + geom_col(col = "gray15", fill = "dodgerblue") +
  theme_bw() +  xlab("Comparisons") + ylab("Review Frequency")
# mean.diff.out <- madata %>% group_by(file.nr, comparison.nr) %>% distinct(outcome.name) %>% 
#   ungroup() %>% group_by(file.nr) %>% 
#   count() %>% ungroup %>% summarise(mean = mean(n))
# 
# median.diff.out <- madata %>% group_by(file.nr, comparison.nr) %>% distinct(outcome.name) %>% 
#   ungroup() %>% group_by(file.nr) %>% 
#   count() %>% ungroup %>% summarise(mean = median(n))
@
\caption{Empirical distribution of number of comparisons per review.}
\label{comparisons.per.review}
\end{figure}

@@

median.diff.out <- madata %>% group_by(file.nr, comparison.nr) %>% distinct(outcome.name) %>% 
  ungroup() %>% group_by(file.nr) %>% 
  count() %>% ungroup %>% summarise(mean = median(n))
@
\caption{Empirical distribution of number of different research subjects per review.}
\label{subjects.per.review}
\end{figure}

>>>>

<<echo=FALSE, results='asis'>>=
tp1 <- arrange(filter(madata, file.nr == 21) %>% 
          select(Study = study.name, Comparison = comparison.name,Outcome = outcome.name), Study)
tp1[tp1$Study == "P\303\251rez-B\303\241rcena 2008", 1] = "Perez-Barcena 2008"
print(xtable(tp1, label = "barbiturates", caption = "Barbiturate and head injury review. In the columns, study names, comparison types and outcome measure of the comparisons are given"), include.rownames = F, size = "footnotesize")
@

@@

\vspace{0mm}
Having provided a rough overview over the dataset, now, some more specific information is provided. The dataset consists of \Sexpr{dim(madata)[1]} comparisons and has \Sexpr{dim(madata)[2]} variables that specify the comparisons. The abundance of some missing values in the dataset is given in Table \ref{missing}. For variables as research subject, outcome and subgroup name and event counts there are no missing values. The relative abundance of missing values is very low except for study years.

@@

print(xtable(missing.table, label = "missing", caption = "Number of missing variables and measurements in the dataset", align = "lr"), include.colnames = F,
      size = "footnotesize", digits = 0)
@

@@

\begin{figure}
<<echo=FALSE>>=
madata %>% filter(study.year < 2019 & study.year > 1920) %>% ggplot(aes(x = study.year)) + geom_histogram(col = "gray15", fill = "dodgerblue") +
  theme_bw() + xlab("Year") + ylab("Study frequency")
@
\caption{Frequencies of study publication years in the dataset. 44655 were excluded due to likely wrong indications}
\label{study.years}
\end{figure}

Figure \ref{study.outcomes} provides the frequencies of outcome types of the comparisons. Note that the abundance of mean differences and standardized mean differences can also give an impression of the proportion of continuous outcome comparisons vs. binary outcome comparisons in the dataset.

\begin{figure}
<<echo=FALSE>>=
yodata %>% group_by(outcome.measure) %>% count() %>% arrange(desc(n)) %>% ungroup() %>% filter(row_number() < 9) %>% 
  ggplot(aes(x = outcome.measure, y = n)) +
  geom_col(col = "gray15", fill = "dodgerblue") +
  theme_bw() + ylab("Comparison frequency") + xlab("Outcome measure")
@
\caption{Frequencies of some outcome measures for the effects in the dataset. 5593 measures with other outcome measures are excluded}
\label{study.outcomes}
\end{figure}

@@

\begin{figure}
<<echo=FALSE>>=
madata %>% group_by(file.nr) %>% distinct(study.name) %>% count() %>%
  filter(n < 50) %>%
  full_join( madata %>% group_by(file.nr) %>% distinct(study.name) %>% count %>%
               filter(n > 49) %>% mutate(n = 50)) %>%
  group_by(n) %>% count() %>%
  ggplot(aes(x = n, y = nn)) + geom_col(col = "gray15", fill = "dodgerblue") +
  theme_bw() + xlab("Study number") + ylab("Reviews Frequency")
@
\caption{Empirical distribution of number of studies per review}
\label{studies.per.review}
\end{figure}

\begin{figure}
<<echo=FALSE>>=
madata %>% group_by(file.nr) %>% count() %>%
  filter(n < 50) %>%
  full_join( madata %>% group_by(file.nr) %>% distinct(comparison.name) %>% count %>%
               filter(n > 49) %>% mutate(n = 50)) %>%
  group_by(n) %>% count() %>%
  ggplot(aes(x = n, y = nn)) + geom_col(col = "gray15", fill = "dodgerblue") +
  theme_bw() +  xlab("Comparisons") + ylab("Review Frequency")
# mean.diff.out <- madata %>% group_by(file.nr, comparison.nr) %>% distinct(outcome.name) %>% 
#   ungroup() %>% group_by(file.nr) %>% 
#   count() %>% ungroup %>% summarise(mean = mean(n))
# 
# median.diff.out <- madata %>% group_by(file.nr, comparison.nr) %>% distinct(outcome.name) %>% 
#   ungroup() %>% group_by(file.nr) %>% 
#   count() %>% ungroup %>% summarise(mean = median(n))
@
\caption{Empirical distribution of number of comparisons per review}
\label{comparisons.per.review}
\end{figure}

@@

median.diff.out <- madata %>% group_by(file.nr, comparison.nr) %>% distinct(outcome.name) %>% 
  ungroup() %>% group_by(file.nr) %>% 
  count() %>% ungroup %>% summarise(mean = median(n))
@
\caption{Empirical distribution of number of different research subjects per review}
\label{subjects.per.review}
\end{figure}
